Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-24 ECCV/paper.tex
Added Design, Algorithm.

\section{Design of Fiducial}

\section{Fiducial Detection Algorithm}
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

\section{Experimental Results}
\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker.
\subsubsection{Comparison with ARTag}
\subsubsection{Comparison with Blut}

>>>>

\section{Design of Fiducial}
Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. The outermost and
innermost rings represent the start and end of the code and is embedded in the
fiducial; these are not considered part of the code itself. The binary code is
represented by the presence (or absence) of rings between ``marker'' rings.
Depending on which ring is present or absent, the resulting binary code will
change. The number of different patterns depends on the number of bits in the
binary code. For example, if the binary code has three bits, there will be a
maximum of three rings between``marker'' rings and we end up with eight
different patterns.

\begin{figure}
\centering
  \includegraphics[width=.2\linewidth]{newconcentric_00.pdf}  
  \includegraphics[width=.2\linewidth]{newconcentric_01.pdf}
  \includegraphics[width=.2\linewidth]{newconcentric_10.pdf}
  \includegraphics[width=.2\linewidth]{newconcentric_11.pdf}
  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
  Binary Code 01, Binary Code 10, Binary Code 11)}
  \label{fig:fiducials}
\end{figure}

\section{Fiducial Detection Algorithm}
Overall flow of fiducial detection algorithm can be summarised as follows:
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave\cite{GaborFilter}. It is used to find high gradient
patches from the image. In our case, it will detect blur invariant sections of the fiducials We
have applied Gabor filter for eight different orientations and then calculated
L2 norm of all outputs.

\textbf{Clustering}: Connected components are found from the Gabor output. 
These connected components are then clustered in hierarchical fashion, to find
the group of closely positioned patches.

\textbf{PCA}: Principal Component Analysis is done on the clustered Gabor
output. Along 1st principal component, intensity profile in the original image is found.
Number of transitions in the intensity profile will give us the number of rings.

\textbf{Classification}: Each synthetic fiducial pattern is blurred along 36
orientations (0, 10, 20, \ldots , 350) and intensity profile along first
principal component from every output is taken as training data for that fiducial pattern.
Training data for patterns having same number of rings is grouped together;
e.g., in two bit binary coded fiducial, training data for pattern “01” and “10”
will be grouped together. Now, depending on the number of detected rings, test
pattern is matched against corresponding training data using K-Nearest Neighbor
Classifier (K=5).

\section{Experimental Validation}
\subsection{Comparison}
We will compare our results with standard fiducials such as ARTag. Also, we will
compare our results with Blur driven tracker.
\subsubsection{Comparison with ARTag}
\subsubsection{Comparison with Blut}
